Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision

### 2015-08-18 latex/paper.tex
ignore .ipynb

While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable. Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence. In both cases, these simulations can be well-fit by a drift-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig. 1E-F).

>>>>

While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable. Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence. In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig. 1E-F).
